---
title: "Cookie Cutter Shop Report"
resource_files:
- cookie-shop-banner.png
- low-inventory-banner.png
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(blastula)
```

## Orders, Sales, and Inventory Level

This is an example report based loosely on a real Etsy shop I once experimented with running. All data is simulated. 

Import data from CSV:

```{r import_data, message=FALSE, warning=FALSE}
library(readr)

cookie_shop_orders <- read_csv("cookie-shop-inventory.csv", 
    col_types = cols(date = col_date(format = "%m/%d/%y")))
```

Summarize the orders data for each filament type: 

```{r sales_tracker, message=FALSE, warning=FALSE}
library(dplyr)

orders <- cookie_shop_orders %>%
  select(purple, black, red, total_orders) %>%
  summarise_all(sum)
```

#### Running count of total shop orders placed: `r orders$total_orders`

### Count of units ordered by color:

- **Purple:** `r orders$purple`
- **Black:** `r orders$black`
- **Red:** `r orders$red`

#### Total units sold: `r orders$purple + orders$black + orders$red`

---

## Inventory Burndown Charts

### Filament color orders and inventory level:

```{r orders_inventory, echo=FALSE, , message=FALSE, warning=FALSE}
library(ggplot2)
library(ggthemes)
library(gridExtra)

p <- cookie_shop_orders %>%
  ggplot() + geom_bar(aes(x = date, y = purple), stat = "identity", color="purple", fill="white") +
  geom_line(aes(x = date, y = p_inventory)) + theme_clean()

b <- cookie_shop_orders %>%
  ggplot() + geom_bar(aes(x = date, y = black), stat = "identity", color="black", fill="white") +
  geom_line(aes(x = date, y = b_inventory)) + theme_clean()

r <- cookie_shop_orders %>%
  ggplot() + geom_bar(aes(x = date, y = red), stat = "identity", color="red", fill="white") +
  geom_line(aes(x = date, y = r_inventory)) + theme_clean()

grid.arrange(p,b,r)
```

### Current inventory by unit color:

```{r current_inventory, echo=FALSE, message=FALSE, warning=FALSE}
library(lubridate)

low_inventory <- FALSE

inventory_levels <- cookie_shop_orders %>% 
  filter(date == today()) %>%
  mutate(p_alert = p_inventory <= 2) %>%
  mutate(b_alert = b_inventory <= 2) %>%
  mutate(r_alert = r_inventory <= 2)

if (inventory_levels$p_alert == TRUE || inventory_levels$b_alert == TRUE || inventory_levels$r_alert == TRUE) {
  low_inventory <- TRUE
}
```

- **Purple:** `r inventory_levels$p_inventory` | **Alert:** `r inventory_levels$p_alert`
- **Black:** `r inventory_levels$b_inventory` | **Alert:** `r inventory_levels$b_alert`
- **Red:** `r inventory_levels$r_inventory` | **Alert:** `r inventory_levels$r_alert`

## Inventory Control

If my shop dips into the "low inventory zone" for any color of cookie cutter, send an email. 

```{r connect_email, echo=FALSE}
if (low_inventory == TRUE) {
  render_connect_email(input = "inventory-alert.Rmd") %>%
    attach_connect_email(
      subject = "Cookie Shop: Low inventory alert!"
    )
} else {
  render_connect_email(input = "inventory-update.Rmd") %>%
    attach_connect_email(
      subject = "Cookie Shop: Orders and Inventory Update"
    )
}
```

